---
title: "Miembros"
---

Miembros del [grupo de Ecoinformática](http://www.aeet.org/es/gruposdetrabajo/ecoinformatica.html) de la [Asociación Española de Ecología Terrestre (AEET)](https://www.aeet.org/es/). 

Para darte de alta rellena tus datos [aquí](https://forms.gle/bkCfSjERcDHsrLhx8). Si quieres actualizar o corregir un error en los datos por favor escribe a ecoinf.aeet@gmail.com.

<br>


```{r}
#| label = "setup",
#| include = FALSE
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE)
```



``` {r echo = F , message = FALSE, warning = F}
# library(dplyr)
# library(sf)
# library(htmltools)

library(leaflet)
source("R/map_functions.R")


# read members' information from google sheet
member.table <- gsheet::gsheet2tbl("19J9P-is9eJWoDN7_agmSeu5S5YgD4JZIoe_FtZ-G3EQ") |>
  format_member_table() |> 
  unique()
  # dplyr::distinct()

# read institution coordinates and only search for the new ones
coords.table <- read.csv("institutioncoords.csv") |> 
  update_coord_table(member.table = member.table) |> 
  unique()
  # dplyr::distinct()

# rewrite updated table of institutions coordinates
write.csv(coords.table, file = "institutioncoords.csv", 
          quote = TRUE, row.names = FALSE, fileEncoding = "UTF-8")

# combine both table by its affiliation and add coordinates (POINTS)
member.table.coords <- merge(member.table, coords.table, all.x = TRUE) |> 
  subset(!is.na(lon))
  # filter(!is.na(lon)) |> 
  # st_as_sf(coords = c("lon", "lat")) |> 
member.table.coords$weblink <- paste0('<a href="', 
                         'https://ecoinfaeet.github.io/new_website/miembros/', 
                         iconv(gsub(" ", "_", member.table.coords$`Nombre y apellidos`), 
                               from = 'UTF-8', to = 'ASCII//TRANSLIT'),
                         ".html",
                         '" target="_blank">', member.table.coords$`Nombre y apellidos`, 
                         '</a>')

# plot map

custom_icon <- leaflet::makeIcon(
  iconUrl = "images/location_custom.png",
  iconWidth = 25, iconHeight = 30,
  iconAnchorX = 12, iconAnchorY = 30
)



leaflet(member.table.coords) |> 
  addTiles(options = providerTileOptions(noWrap = TRUE)) |> 
  addMarkers(popup = ~(weblink), 
             label = member.table.coords$`Nombre y apellidos`,
             # labelOptions = labelOptions(zoomAnimation = TRUE),  # deprecated
             clusterOptions = markerClusterOptions(),
             icon = custom_icon)
  
  
```
<br>
<br>



```{r miembros, include=F, echo = F}

formdata <- gsheet::gsheet2tbl("https://docs.google.com/spreadsheets/d/19J9P-is9eJWoDN7_agmSeu5S5YgD4JZIoe_FtZ-G3EQ/edit?usp=sharing")
source("R/miembros_functions.R")

for (i in 1:nrow(formdata)){
  name <- formdata[i,"Nombre y apellidos", drop=TRUE] |> 
    gsub(pattern = " ", replacement = "_") |> 
    iconv(from = 'UTF-8', to = 'ASCII//TRANSLIT')
  if (file.exists(paste0("miembros/", name, ".qmd"))) {next}
create_profile_qmd(formdata, i)
}


```

---
# title: "Participantes"
listing:
  - id: miembros
    contents: "miembros/*.qmd"
    type: grid
    image-height: 225px
    grid-columns: 6
    sort: sortby
    fields: [image, title]
    grid-item-align: center
    
---

:::{#map}
:::

:::{#equipo}
:::
